---
title: "Technical Appendix"
author: "Ilayda Dinc & Sara Orofino"
date: "5/28/2019"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
# Packages and data

library(tidyverse)
library(janitor)
library(ggplot2)
library(knitr)
library(ggrepel)
library(ggpubr)
library(gridExtra)
library(extrafont)

carbon <- read_csv("HW4Data.csv") %>% 
  clean_names()

```

###1. Marginal Cost of Abatement by Sector 

Using the data provided, regression analysis is conducted to find the marginal cost of abatement curve for 4 different sectors. For the ease of later calculations, linear models are used for each sector. However, there might be better fitting functional forms. For example, for Sector C exponential function might fit better, and for Sector D quadratic function might fit better.

####Sector A

```{r, include=FALSE, message=FALSE}
# First make trial graph to see what function it might be 
trial_a <- ggplot(carbon, aes(x=abatement, y=mc_a)) +
  geom_point() +
  geom_smooth()

trial_a 

# Looks linear

# Use linear regression to find the equation of the line

a_lm <- lm(mc_a ~ abatement, data=carbon)

# Store coefficients of regression
int_a <- a_lm$coefficients[1]
slope_a <- a_lm$coefficients[2]

 
```

$Marginal~Cost~Abatement~Sector~A = `r slope_a`*q + `r int_a`$  

####Sector B

```{r, include=FALSE, message=FALSE}

# First make trial graph to see what function it might be

# sam is gonna use linear
trial_b <- ggplot(carbon, aes(x=abatement, y=mc_b)) +
  geom_point() +
  geom_smooth()

trial_b

# Try fitting linear regression

b_lm <- lm(mc_b ~ abatement, data = carbon)

# Graph it to check the fit 
b_lm_graph <- ggplot(carbon, aes(x=abatement, y=mc_b)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x)

b_lm_graph


# Fit looks okay - save the regression coefficients
int_b <- b_lm$coefficients[1]
slope_b <- b_lm$coefficients[2]


```

$Marginal~Cost~Abatement~Sector~B = `r slope_b`*q + `r int_b`$


####Sector C

```{r, include=FALSE, message=FALSE}
# First make trial graph to see what function it might be
trial_c <- ggplot(carbon, aes(x=abatement, y=mc_c)) +
  geom_point() +
  geom_smooth()

trial_c

c_lm <- lm(mc_c ~ abatement, data = carbon)

# save the regression coefficients
int_c <- c_lm$coefficients[1]
slope_c <- c_lm$coefficients[2]


```

$Marginal~Cost~Abatement~Sector~C = `r slope_c`*q + `r int_c`$

####Sector D

```{r, include=FALSE, message=FALSE}
# First make trial graph to see what function it might be
trial_d <- ggplot(carbon, aes(x=abatement, y=mc_d)) +
  geom_point() +
  geom_smooth()

trial_d

# Trying quadratic

d_lm <- lm(mc_d ~ abatement+I(abatement^2), data = carbon)

int_d <- d_lm$coefficients[1]
c1_d <- d_lm$coefficients[2]
c2_d <- d_lm$coefficients[3]


d_lm_graph <- ggplot(carbon, aes(x=abatement, y=mc_d)) +
  geom_point() + 
  geom_smooth(method = "lm", formula = y~x+I(x^2))

d_lm_graph

# quadratic looks good to me

# trying linear

linear_d <- lm(mc_d ~ abatement, data = carbon)

int_lineard <- linear_d$coefficients[1]
slope_d <- linear_d$coefficients[2]



```
For linear fit: $Marginal~Cost~Abatement~Sector~D = `r slope_d`*q +`r int_lineard`$

Quadratic fit for Sector D's marginal abatement cost is found to be:
$Marginal~Cost~Abatement~Sector~D = `r c1_d`*q + `r c2_d`*q^2 +`r int_d`$

The estimated marginal abatement cost functions in all four sectors are graphed below in Figure 1
```{r echo=FALSE, fig.width= 4.5, fig.height= 4.5}

###### Graph of all sectors

all_sectors <- ggplot(carbon, aes(x=abatement)) +
  geom_smooth(aes(y=mc_a), method = lm, se = FALSE, size = 0.5, color = "red") + 
  geom_smooth(aes(y=mc_b), method = lm, se = FALSE, size = 0.5, color = "blue") +
  geom_smooth(aes(y=mc_c), method = lm, se = FALSE, size = 0.5, color = "green") +
  geom_smooth(aes(y=mc_d), method = lm, se = FALSE, size = 0.5, color = "purple") +
  theme_classic()+
  labs(x ="Abatement (tons)",
       y ="Price($/ton)")+
  scale_x_continuous(expand = c(0,0))+
  theme(text=element_text(size=12,family="Times New Roman"))
  

all_sectors

# I can't find a way to add legend

```


*Figure 1:* Marginal Abatement Cost Funtions of Four Sectors

###2. Demand for Carbon Emissions 

```{r, include=FALSE}

####### Sector A Demand Curve:  
# Current emissions are 180 - use quantities from 0 to 180 by 10
quantity_a <- seq(0,180,by=10)


# Write function for demand curve for Sector A

d_a <- function(q){
  (slope_a*(180-q)) + int_a
}

# Derive demand curve using the values above
demand_a <- d_a(quantity_a)

# Graph it to see if this worked....
curve(d_a, from=0, to=180, xlab = "x", ylab = "y")

# willing to pay 95.2 for the first ton of emissions 


######## Sector B Demand Curve:  

# Current emissions are 200 - use quantities from 0 to 200 by 10
quantity_b <- seq(0,200,by=10)

# Write function for demand curve for Sector B

d_b <- function(q){
  (slope_b*(200-q) + int_b)
}

# Graph it 
curve(d_b, from=0, to=200, xlab = "x", ylab = "y")

# Plug in quantities into function to check
demand_b <- d_b(quantity_b)


######## Sector C Demand Curve: 

# Current emissions are 220 - use quantities from 0 to 220 by 10
quantity_c <- seq(0,220,by=10)

# Write function for demand curve for Sector C

d_c <- function(q){
  (slope_c*(220-q) + int_c)
}

# Graph it 
curve(d_c, from=0, to=220, xlab = "x", ylab = "y")

# Plug in quantities into function to check
demand_c <- d_c(quantity_c)


######## Sector D Demand Curve:  
quantity_d <- seq(0,300, by=10)

d_d <- function(q){
  (slope_d*(300-q) + int_lineard)
}


```

*Demand Curves*  

Demand curve for carbon emissions is found for each sector by pluging in (Current Emission-q) for q in the marginal cost of abatement equation. The cost of abatement of quantity q is equal to willingness to pay for emitting (Current Emission-q). 

In the new equation (demand curve), q will represent the amount of emissions. Plugging in O for q will result in the willingness to pay for the right to emit the first unit.

Sector A:  $Price~of~Emissions = `r slope_a`*(180-q) + `r int_a`$  
 - Willingness to Pay for First Unit = \$95.2    

Sector B:  

$Price~of~Emissions = `r slope_b`*(200-q) + `r int_b`$  

- Willingness to Pay for First Unit = \$49.12 

Sector C:

$Price~of~Emissions = `r slope_c`*(220-q) + `r int_c`$  

- Willingness to Pay for First Unit = \$160.78

Sector D:

$Price~of~Emissions = `r slope_d`*(300-q) +`r int_lineard`$   

- Willingness to Pay with Linear Function: \$87.69 

$Price~of~Emissions = `r c1_d`*(300-q) + `r c2_d`*(300-q)^2 +`r int_d`$  

- Willingness to Pay for First Unit = \$185.46  

Note: The rest of the anlaysis will use the linear demand equations for each sector. But it is important to note that different functional forms result in different predictions for willingness to pay.   

###3. Country X

Suppose to meet the Paris Accord commitments, Country X (which contains sectors A, B, and C) needs to cut all carbon emissions in half.

####a. Cap on Carbon  

```{r include=FALSE}

# Each sector cuts emissions by 100 - abates 100 
################# Part 1 Write abatement curve functions for each sector and plug in 100 for Q

#### Abatement function Sector A

abate_a <- function(q){
  (slope_a*q) + int_a
}

costa_100 <- abate_a(100) 

#### Abatement function Sector B

abate_b <- function(q){
  (slope_b*q) + int_b
}

costb_100 <- abate_b(100)

#### Abatement function Sector C

abate_c <- function(q){
  (slope_c*q) + int_c
}

costc_100 <- abate_c(100)

#### Abatement function Sector D - NOT used in this question

abate_d <- function(q){
  (slope_d*q) + int_lineard
}

################## Part 2 Integrate to find the area under the curve (the cost of abatement from 0-100)

areaa_100 <- integrate(abate_a, lower = 0, upper = 100)$value

areab_100 <- integrate(abate_b, lower = 0, upper = 100)$value

areac_100 <- integrate(abate_c, lower = 0, upper = 100)$value

################## Part 3 Add all areas together to find the total cost of abating 100 units from each sector

totalcost_100 <- areaa_100 + areab_100 + areac_100
```

Marginal cost of abatement curves for each sector are used to calculate the total cost of abating by 100 tons. The area underneath the marginal cost of abatement curve from 0 to 100 gives the total cost of abatement for that sector. The arees are calculated by integration and the total cost of carbon cap is the sum of the costs of three sectors.

1. Total Cost of Carbon Cap     

$Total~Cost = `r round(totalcost_100, digits=2)`$   

2. Cost/Benefits to each Sector      

$Cost~to~Sector~A = `r round(areaa_100, digits=2)`$    

$Cost~to~Sector~B = `r round(areab_100, digits=2)`$    

$Cost~to~Sector~C = `r round(areac_100, digits=2)`$    

3. Tax Revenue  

There is no tax revenue with a carbon cap.

####b. Tax on Carbon 

```{r include= FALSE}

### Switch slope and intercept of A to be in terms of q
qint_a <- (-int_a/slope_a)
qslope_a <- (1/slope_a)
qa_abate <- function(p){qint_a + (qslope_a*p)}

### Switch slope and intercept of B to be in terms of q
qint_b <- (-int_b/slope_b)
qslope_b <- (1/slope_b)
qb_abate <- function(p){qint_b + (qslope_b*p)}

### Switch slope and intercept of C to be in terms of q 
qint_c <- (-int_c/slope_c)
qslope_c <- (1/slope_c)
qc_abate <- function(p){qint_c + (qslope_c*p)}

##### Aggregate marginal cost of abatement curves: 
# Sector C has lowest intercept - find the quantity where C and A intersect (Kink Point 1)
kink1_q <- qint_c+qslope_c*int_a
# Sector A/C lines cross at q=14.5

# From the graph above Sector C has the lowest intercept followed by sector A; aggregate these two first 
agg_intq_ca <- qint_c + qint_a
agg_slopeq_ca <- qslope_c + qslope_a


agg_ac <- function(q){
  ((1/agg_slopeq_ca)*q) + (abs(agg_intq_ca)/agg_slopeq_ca)
}

# Kink point 2: where price = intercept B (9.32) plugged into the agg C/A curve
kink2_q <- agg_intq_ca + (agg_slopeq_ca*int_b)
# 300 abated will be the aggregate of all three curves since it's past the second kink point 

# Aggregate B with the aggregated C/A
agg_intq_all <- agg_intq_ca + qint_b
agg_slopeq_all <- agg_slopeq_ca + qslope_b

# Put in terms of price:
agg_abate <- function(q){
  ((1/agg_slopeq_all)*q) + (abs(agg_intq_all)/agg_slopeq_all)
}

# Plug in 300 to find the price of the tax 
optimal_tax <- agg_abate(300)

###### Find how much each sector abates and the cost using the optimal tax 

# Sector A 
qtax_a <- qa_abate(optimal_tax) #abates 83.3 
costa_tax <- integrate(abate_a, lower = 0, upper = qtax_a)$value + ((180-83.3)*optimal_tax)


# Sector B 
qtax_b <- qb_abate(optimal_tax) #abates 151.5
costb_tax <- integrate(abate_b, lower = 0, upper = qtax_b)$value + ((200-151.5)*optimal_tax)

# Sector C 
qtax_c <- qc_abate(optimal_tax) # abates 65.2
costc_tax <- integrate(abate_c, lower = 0, upper = qtax_c)$value + ((220-65.2)*optimal_tax)

# Aggregated cost #abates 300, emits 300
costagg_tax_abatement<-integrate(abate_c, lower = 0, upper = qtax_c)$value+ integrate(abate_b, lower = 0, upper = qtax_b)$value+  integrate(abate_a, lower = 0, upper = qtax_a)$value

costagg_tax <- costa_tax+costb_tax+ costc_tax
  
#integrate(agg_abate, lower = 0, upper = 300)$value+ (300*optimal_tax)

####### Find Tax Revenue 
tax_rev <- optimal_tax*300

```

To find the tax that accomplishes the desired reduction of 300, aggreagate marginal cost curve for 3 sectors in Country X is found. to find the aggregate cost, the marginal costs equations of 3 sectors are horizontally added. Marginal cost of 300th unit on the aggregate marginal cost curve is equal to the tax required.

$Optimal~Carbon~Tax = `r round(optimal_tax, digits=2)`$ 

1. Total Cost of Carbon Tax    

The total abatement cost is the area under the aggregate cost curve from 0 to 300.each sector also pays tax for their emissions, so the amount paid for tax is added to the total abatement cost.

$Total~Abatement~Cost~of~Carbon~Tax = `r round(costagg_tax_abatement, digits=2)`$  

Each sector also pays tax for their emissions, so the amount paid for tax is added to the total abatement cost. The cost of meeting the target with carbon tax is calculated as:

$Total~Cost~Carbon~Tax = `r round(costagg_tax, digits=2)`$  


2. Cost/Benefits to each Sector    

Plugging in the marginal cost of abatement(the tax in the case) will result in the quantity abated by each sector. The areas underneath the marginal cost curves for each sector from 0 to the quantity abated will give the total cost of abatement for each sector. Each sector also pays tax for their emissions, so the amount of tax each sector pays is added to their total cost.


$Cost~to~Sector~A = `r round(costa_tax, digits=2)`$        

$Cost~to~Sector~B = `r round(costb_tax, digits=2)`$        

$Cost~to~Sector~C = `r round(costc_tax, digits=2)`$  

  

3. Tax Revenue    

Tax revenue is calculated by multiplying the total emissions by the amount of tax. Total emissions is found by subtracting the amount of abatement from the total initial emissions of 600 tons.

$Tax~Revenue = `r round(tax_rev, digits=5)`$    

####c. Cap and Trade  

Even though they are initially allocated current emissions minus 100, cap and trade will satisfy the equal marginal principle and the total reduction of 300 will be distributed between the three sectors just like in the part b. The marginal cost of abatement will be equal for all sectors which is equal to the marginal cost of abatement of 300th unit on the aggregate cost curve.

1. Total Cost of Carbon Cap and Trade     

The total cost of the cap and trade is the area under the aggregate cost curve from 0 to 300. The trades between sectors cancel each other.
```{r include=FALSE}
# Sector A 
#abates 83.3 , buys 16.7 from Sector B
costa_cap <- integrate(abate_a, lower = 0, upper = qtax_a)$value + (16.7*optimal_tax)


# Sector B 
 #abates 151.5, sells 51.5 to A and C
costb_cap <- integrate(abate_b, lower = 0, upper = qtax_b)$value - (51.5*optimal_tax)

# Sector C 
# abates 65.2, buys 34.8 from B
costc_cap <- integrate(abate_c, lower = 0, upper = qtax_c)$value + (34.8*optimal_tax)


costagg_cap<-costa_cap+costb_cap+costc_cap

```
$Total~Cost~Cap~and~Trade = `r round(costagg_cap, digits=2)`$  

2. Cost/Benefits to each Sector  

Firstly, The areas underneath the marginal cost curves for each sector from 0 to the quantity abated are calculated to find total cost of abatement for each sector. Then, depending on the trade, the quantity traded times the price is added (if bought) or subtracted (if sold) to find the total cost of Cap and Trade to each sector.


$Cost~to~Sector~A = `r round(costa_cap, digits=2)`$      

$Cost~to~Sector~B = `r round(costb_cap, digits=2)`$      

$Cost~to~Sector~C = `r round(costc_cap, digits=2)`$  
   

3. Tax Revenue    

There is no tax revenue with a cap and trade.  


###4. Country Y

Country Y contains only Sector D and is not obligated to reduce its emissions. To enter into Country X's carbon market Country Y would need to cap its emissions at its current level (300 tons) but allows them to sell credits to Sectors A, B, and C in Country X.     


```{r include = FALSE}


qint_d <- (-int_lineard/slope_d)
qslope_d <- (1/slope_d)

agg_intq_xy <- agg_intq_all + qint_d
agg_slopeq_xy <- agg_slopeq_all + qslope_d

# Put in terms of price:
agg_abate_xy <- function(q){
  ((1/agg_slopeq_xy)*q) + (abs(agg_intq_xy)/agg_slopeq_xy)
}

# Plug in 300 to find the price of the tax 
cost_xy <- agg_abate_xy(300)

qd_abate <- function(p){qint_d + (qslope_d*p)}
q_xy_d <- qd_abate(cost_xy)



qxy_a <- qa_abate(cost_xy) #abates 66.7, buys  
costa_xy <- integrate(abate_a, lower = 0, upper = qxy_a)$value + ((100-66.7)*cost_xy)


# Sector B 
qxy_b <- qb_abate(cost_xy) #abates 103, sells
costb_xy <- integrate(abate_b, lower = 0, upper = qxy_b)$value - (3*cost_xy)

# Sector C 
qxy_c <- qc_abate(cost_xy) # abates 52.9 buys
costc_xy <- integrate(abate_c, lower = 0, upper = qxy_c)$value + ((100-52.9)*cost_xy)

#Sector D

qxy_d <- qd_abate(cost_xy) # abates 77.4 - sells all
costd_xy <- integrate(abate_d, lower = 0, upper = qxy_d)$value - (77.4*cost_xy)

costagg_xy<-costa_xy+costb_xy+costc_xy+costd_xy

costagg_xy_tox<-costa_xy+costb_xy+costc_xy
#kink3_q <- agg_intq_all + (agg_slopeq_all*int_lineard)


#costagg_xy2 <- integrate(abate_c, lower = 0 , upper = 3.84)$value+ integrate(agg_ac, lower = 3.84, upper =57.9)$value+ integrate(agg_abate, lower = 57.9, upper = 60.9)$value+ integrate(agg_abate_xy, lower = 60.9, upper = 300)$value

```

Sector D is also added to the aggregate marginal cost curve and abatement quantity of 300 is plugged into the equation. That will result in the marginal cost of `r round(cost_xy, digits=2)`  which is less than the marginal cost of abatement for Country X only ( `r round(optimal_tax, digits=2)` ). Then the total cost of abatement of 300 is calculated to be `r round(costagg_xy, digits=2)` by adding up costs to each sector.

Also, total cost of international cap and trade to Country X is calculated as $`r round(costagg_xy_tox, digits=2)`, whereas total cost to Country Y is `r round(costd_xy, digits=2)`.

Incentives for Country Y to enter the carbon market:  

The total cost of entering the market is negative for Country Y. It is cheaper for Sector D to reduce their emissions and the sectors in country X are willing to pay more than the cost of sector D.


Incentives for Country X to attract Country Y to the carbon market:  

The total cost of cap and trade for Country X gets cheaper as Country Y enters the market. (It was $`r round(costagg_cap, digits=2)` for the cap and trade in only Country X) Sector D can reduce their emission cheaper than the sectors in Country X. So, they are going to pay less to Country Y than whatever that would normally cost to them to reduce.


###5. Local Air Pollution  

Now assume every ton of carbon emissions creates one ton of local air pollution. Local air pollution only causes economic damages in the country where it is emitted. Neither Country X nor Country Y have local air pollution regulations.  

####a. Carbon Cap and Trade Market only Covering Country X  

How much local air pollution would you expect in Country X and Country Y?  

- If Cap and Trade is only covering country X, country X will be emitting 300 tons of carbon emissions and that will result in 300 tons of local air pollution.

- Since there is no cap and trade in country Y, they will continue to emit at the same level as their current emissions which is 300 tons of carbon, and that will result in 300 tons of air pollution.


####b. Country Y enters the Carbon Market of Country X  

How much local air pollution would you expect in Country X and Country Y?  

```{r include=FALSE}
total_emission_x <- 300+q_xy_d
```

From the previous question, the abatement of country Y is calculated as `r round(q_xy_d, digits=2)`, if it enters the carbon market. So, Country X will be emitting `r round(q_xy_d, digits=2)` more, so the amount of air pollution will be `r round(total_emission_x, digits=2)`.

```{r include=FALSE}
total_emission_y <- 300-q_xy_d
```

Since the Country Y will be abating their current emissions of 300 tons by `r round(q_xy_d, digits=2)`, they will be emitting `r round(total_emission_y, digits=2)` tons of carbon, and that will result in `r round(total_emission_y, digits=2)` tons of air pollution.


####c. Advice on International Trade of Carbon Emission Credits  

Allowing international trade of carbon emissions is economically efficient for both countries but the local impacts of carbon emissions is not captured by this model. If Country Y enters to the market, Country X will be emitting more carbon which will cause a lot of local air pollution.