---
title: "Technical Appendix"
author: "Ilayda Dinc & Sara Orofino"
date: "5/28/2019"
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE}
# Packages and data

library(tidyverse)
library(janitor)

carbon <- read_csv("HW4Data.csv") %>% 
  clean_names()

```

###1. Marginal Cost of Abatement by Sector 

####Sector A

```{r, include=FALSE, message=FALSE}



```


####Sector B

```{r, include=FALSE, message=FALSE}



```


####Sector C

```{r, include=FALSE, message=FALSE}



```



####Sector D

```{r, include=FALSE, message=FALSE}



```

###2. Demand for Carbon Emissions 



###3. Country X

Suppose to meet the Paris Accord commitments, Country X (which contains sectors A, B, and C) needs to cut all carbon emissions in half. For each policy option derive the following:  
1. The total cost of meeting the target in Country X  
2. The cost (or benefit) to each sector  
3. The tax revenue generated  

####a. Cap on Carbon  




1. Total Cost of Carbon Cap   

2. Cost/Benefits to each Sector  

3. Tax Revenue  

####b. Tax on Carbon 



1. Total Cost of Carbon Cap     

2. Cost/Benefits to each Sector    

3. Tax Revenue    


####c. Cap and Trade  




1. Total Cost of Carbon Cap     

2. Cost/Benefits to each Sector    

3. Tax Revenue    



###4. Country Y

Country Y contains only Sector D and is not obligated to reduce its emissions. To enter into Country X's carbon market Country Y would need to cap its emissions at its current level (300 tons) but allows them to sell credits to Sectors A, B, and C in Country X.   

Incentives for Country Y to enter the carbon market:  


Incentives for Country X to attract Country Y to the carbon market:  


###5. Local Air Pollution  

Now assume every ton of carbon emissions creates one ton of local air pollution. Local air pollution only causes economic damages in the country where it is emitted. Neither Country X nor Country Y have local air pollution regulations.  

####a. Carbon Cap and Trade Market only Covering Country X  

How much local air pollution would you expect in Country X and Country Y?  



####b. Country Y enters the Carbon Market of Country X  

How much local air pollution would you expect in Country X and Country Y?  




####c. Advice on International Trade of Carbon Emission Credits  

